---
title: "Map"
output: html_document
---

## Maps for Boston University
```{r, echo=FALSE, message=FALSE}
library(tigris)
library(sp)
library(rgeos)
library(ggmap)
```

Determines the appropriate longitude/latitude coordinate for the boston university.
```{r, message=FALSE}
geocode("boston university")
```

Get_map provides the same spatial extent for Google Maps (top) and OpenStreetMaps
(bottom) with a single simple syntax, even though their APIs are quite different.

```{r, echo=FALSE, message=FALSE}
bu <- "boston university"
qmap(bu, zoom = 14)
qmap(bu, zoom = 14, source = "osm")
```

Stamen tile sets maptype = "watercolor" and maptype = "toner".
```{r, echo=FALSE, message=FALSE}
qmap(bu, zoom = 14, source = "stamen", maptype = "watercolor")
qmap(bu, zoom = 14, source = "stamen", maptype = "toner")
```

Create Leaflet maps for Boston University.
```{r,echo=FALSE, message=FALSE}
library(leaflet)
m <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(-71.1054, 42.3505, popup="Boston University")
m  # Print the map
```

```{r,echo=FALSE, message=FALSE}
leaflet() %>% addTiles() %>%
  addPopups(-71.1054,42.3505, popup="Boston University",
    options = popupOptions(closeButton = FALSE))
```

## Maps for Boston
Setting extent = "normal" in ggmap illustrates how maps in ggmap are simply ggplot2
graphics.
```{r, echo=FALSE, message=FALSE}
bos <- get_map(location = "boston")
ggmap(bos, extent = "normal")
```

Accessing Google Maps API features with get_googlemap.
```{r, echo=FALSE, message=FALSE}
geocode("boston")
set.seed(500)
df <- round(data.frame(
  x = jitter(rep(-71.06, 50), amount = .3),
  y = jitter(rep(42.36, 50), amount = .3)
), digits = 2)
map <- get_googlemap('boston', markers = df, path = df, scale = 2)
ggmap(map, extent = 'device')
```

